\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\title{Tetris program Documentation}
\author{Wholemew}
\date{\today}

\begin{document}

\maketitle
\tableofcontents

\section{tetris.h}
\subsection{Function: \texttt{parceInput}}
\begin{itemize}
    \item \textbf{Description:} Parses user input and returns the corresponding action.
\end{itemize}

\section{tetrisGUI.h}
\subsection{Function: \texttt{StartingScreen}}
\begin{itemize}
    \item \textbf{Description:} Draws the starting screen of the game.
\end{itemize}

\subsection{Function: \texttt{UpdateGameScreen}}
\begin{itemize}
    \item \textbf{Description:} Draws the in-game screen.
\end{itemize}

\subsection{Function: \texttt{EndGameScreen}}
\begin{itemize}
    \item \textbf{Description:} Draws the endgame screen.
\end{itemize}

\subsection{Function: \texttt{DrawNext}}
\begin{itemize}
    \item \textbf{Description:} Draws the next piece in the designated field.
\end{itemize}

\subsection{Function: \texttt{DrawLine}}
\begin{itemize}
    \item \textbf{Description:} Draws a line shape.
\end{itemize}

\subsection{Function: \texttt{DrawLA}}
\begin{itemize}
    \item \textbf{Description:} Draws a left angle shape.
\end{itemize}

\subsection{Function: \texttt{DrawRA}}
\begin{itemize}
    \item \textbf{Description:} Draws a right angle shape.
\end{itemize}

\subsection{Function: \texttt{DrawLZ}}
\begin{itemize}
    \item \textbf{Description:} Draws a left zigzag shape.
\end{itemize}

\subsection{Function: \texttt{DrawRZ}}
\begin{itemize}
    \item \textbf{Description:} Draws a right zigzag shape.
\end{itemize}

\subsection{Function: \texttt{DrawSquare}}
\begin{itemize}
    \item \textbf{Description:} Draws a square shape.
\end{itemize}

\subsection{Function: \texttt{DrawT}}
\begin{itemize}
    \item \textbf{Description:} Draws a T shape.
\end{itemize}

\section{library.h}
\subsection{Macros: \texttt{WID}}
\begin{itemize}
    \item \textbf{Description:} Width of playing field.
\end{itemize}

\subsection{Macros: \texttt{HEI}}
\begin{itemize}
    \item \textbf{Description:} Height of playing field.
\end{itemize}

\subsection{Macros: \texttt{MAXU}}
\begin{itemize}
    \item \textbf{Description:} Maximum value of unsigned.
\end{itemize}

\subsection{Macros: \texttt{EMP}}
\begin{itemize}
    \item \textbf{Description:} Code of empty space in the field.
\end{itemize}

\subsection{Macros: \texttt{FIL}}
\begin{itemize}
    \item \textbf{Description:} Code of filled space in the field.
\end{itemize}

\subsection{Enum: \texttt{UserAction\_t}}
\begin{itemize}
    \item \textbf{Description:} Types of user actions that may happen in the game.
\end{itemize}

\subsection{Enum: \texttt{Figure\_t}}
\begin{itemize}
    \item \textbf{Description:} Types of figures that may be generated in the game.
\end{itemize}

\subsection{Struct: \texttt{Falling\_t}}
\begin{itemize}
    \item \textbf{Description:} Description of falling figure.
\end{itemize}

\subsection{Struct: \texttt{GameInfo\_t}}
\begin{itemize}
    \item \textbf{Description:} General state of the current game.
\end{itemize}

\subsection{Function: \texttt{Init}}
\begin{itemize}
    \item \textbf{Description:} Initiates the game field and sets up the game at the starting screen.
\end{itemize}

\subsection{Function: \texttt{Destroy}}
\begin{itemize}
    \item \textbf{Description:} Frees memory allocated in the static structure.
\end{itemize}

\subsection{Function: \texttt{StartGame}}
\begin{itemize}
    \item \textbf{Description:} Starts a new game.
\end{itemize}

\subsection{Function: \texttt{userInput}}
\begin{itemize}
    \item \textbf{Description:} Reads user input and handles game consequences.
\end{itemize}

\subsection{Function: \texttt{updateCurrentState}}
\begin{itemize}
    \item \textbf{Description:} Returns the current static game info structure for GUI.
\end{itemize}

\subsection{Function: \texttt{PauseResume}}
\begin{itemize}
    \item \textbf{Description:} Pauses or resumes the game.
\end{itemize}

\subsection{Function: \texttt{EndGame}}
\begin{itemize}
    \item \textbf{Description:} Ends the game and updates the high score.
\end{itemize}

\subsection{Function: \texttt{ShiftLeft}}
\begin{itemize}
    \item \textbf{Description:} Adjusts function to shift the piece to the left.
\end{itemize}

\subsection{Function: \texttt{ShiftRight}}
\begin{itemize}
    \item \textbf{Description:} Adjusts function to shift the piece to the right.
\end{itemize}

\subsection{Function: \texttt{Rotate}}
\begin{itemize}
    \item \textbf{Description:} Adjusts function to rotate the piece.
\end{itemize}

\subsection{Function: \texttt{PutPiece}}
\begin{itemize}
    \item \textbf{Description:} Adjusts function to draw the piece into the field.
\end{itemize}

\subsection{Function: \texttt{CleanPiece}}
\begin{itemize}
    \item \textbf{Description:} Adjusts function to erase the piece from the field.
\end{itemize}

\subsection{Function: \texttt{Drop}}
\begin{itemize}
    \item \textbf{Description:} Drops the piece down until it connects.
\end{itemize}

\subsection{Function: \texttt{MoveDown}}
\begin{itemize}
    \item \textbf{Description:} Moves the piece one step down.
\end{itemize}

\subsection{Function: \texttt{GenerateNext}}
\begin{itemize}
    \item \textbf{Description:} Generates the type of the next piece.
\end{itemize}

\subsection{Function: \texttt{Spawn}}
\begin{itemize}
    \item \textbf{Description:} Spawns next piece in the field and generates new next.
\end{itemize}

\subsection{Function: \texttt{Connect}}
\begin{itemize}
    \item \textbf{Description:} Adjusts function to check the connection of the piece.
\end{itemize}

\subsection{Function: \texttt{CheckEnd}}
\begin{itemize}
    \item \textbf{Description:} Adjusts function to check if the game has ended.
\end{itemize}

\subsection{Function: \texttt{MovePiece}}
\begin{itemize}
    \item \textbf{Description:} Moves piece by a given shift in x and y.
\end{itemize}

\subsection{Function: \texttt{CheckApplyScore}}
\begin{itemize}
    \item \textbf{Description:} Checks and removes the filled rows and updates score.
\end{itemize}

\subsection{Function: \texttt{updateLevel}}
\begin{itemize}
    \item \textbf{Description:} Updates level and speed.
\end{itemize}

\subsection{Function: \texttt{RemoveRow}}
\begin{itemize}
    \item \textbf{Description:} Removes row on r coordinate and shifts upper rows one position down.
\end{itemize}

\subsection{Functions for shifting and rotating specific shapes}
\begin{itemize}
    \item \textbf{Examples:} \texttt{LiShiftLeft}, \texttt{LAShiftLeft}, \texttt{LZShiftLeft}, \texttt{SqShiftLeft}, \texttt{TShiftLeft}, etc.
    \item \textbf{Description:} Shift left/right or rotate specific shape types.
\end{itemize}

\subsection{Functions for shape connection checks}
\begin{itemize}
    \item \textbf{Examples:} \texttt{LiConnect}, \texttt{LAConnect}, etc.
    \item \textbf{Description:} Check if the specific shape is connected.
\end{itemize}

\subsection{Functions for spawn end checks}
\begin{itemize}
    \item \textbf{Examples:} \texttt{LiCheckEnd}, \texttt{LACheckEnd}, etc.
    \item \textbf{Description:} Check if spawning a shape ends the game.
\end{itemize}

\end{document}
